### 2016-01-18 papers/CAFe/HIPS-paper/intro.tex
Removed over emphasis on OCR.

Another option is to abandon the stricture of message passing within a procedural
programming language altogether.  The Open Community Runtime (OCR)
project\cite{OCR:wiki:url} provides an asynchronous task-based runtime designed for
machines with high-core count\cite{Dokulil20151453}, such as can be expected in any
exascale hardware design.  The project's goal is to create a framework and reference
implementation to help developers explore programming methods to improve the power
efficiency, programmability, and reliability of HPC applications while maintaining
application performance.

OCR helps the application developer with the complex process of writing multi-core
applications.  It does this by providing facilities for creating and executing a set of
tasks.  The OCR runtime schedules the execution of these tasks based on events which
embody dataflow and code flow dependencies; when all of the dependencies for a task are
satisfied, the task can be run.

However, it cannot be emphasized too strongly that like using the OpenCL programming
environment, actually creating real scientific applications based on OCR is a high hurdle
for the application developer.  A goal of this paper is to examine ways in
which high-level syntax based on Fortran coarrays can be utilized by compiler-based tools
to \emph{target} programming environments like OpenCL or OCR --- thus freeing the developer from
the task of frequently porting the application to new complex environments.  The hope is
that high-level syntax can hide the complexities of the underlying software and hardware.

@@

In this paper we propose CAFe: \emph{Co-Array Fortran Extensions}.  These extensions to CAF introduce
relatively minor additions to the existing coarray portion of the Fortran language.  They
include the concept of subimages in order to nest coarray images, semantics for distributed
array declarations, memory placement, remote memory transfer, and remote task execution
and synchronization.  CAFe
builds upon the existing standardized coarray features of Fortran.  We will introduce the
proposed CAFe extensions, define their semantics, demonstrate their use in simple
examples, and provide experimental results demonstrating their performance in a prototype implementation.
CAFe is complementary to
previous work extending coarray Fortran\cite{mellor-crummey:2009:caf2,jin:2011:caf2}.

>>>>

Another potential option is to abandon the stricture of message passing within a procedural
programming language altogether.  For example, the Open Community Runtime (OCR)
project\cite{OCR:wiki:url} provides an asynchronous task-based runtime designed for
machines with high-core count\cite{Dokulil20151453}, such as can be expected in any
exascale hardware design.  The project's goal is to create a framework and reference
implementation to help developers explore programming methods to improve the power
efficiency, programmability, and reliability of HPC applications while maintaining
application performance.

\begin{comment}
OCR helps the application developer with the complex process of writing multi-core
applications.  It does this by providing facilities for creating and executing a set of
tasks.  The OCR runtime schedules the execution of these tasks based on events which
embody dataflow and code flow dependencies; when all of the dependencies for a task are
satisfied, the task can be run.
\end{comment}

It cannot be emphasized too strongly that using the OpenCL programming language and
libraries (or programming for the OCR environment) presents a high hurdle for the
application developer creating real scientific applications.  A goal of this paper is to
examine ways in which high-level syntax based on Fortran coarrays can be utilized by
compiler-based tools to \emph{target} programming environments like OpenCL, thus
freeing the developer from the task of frequently porting the application to new complex
environments.  The hope is that high-level syntax can hide the complexities of the
underlying hardware \emph{and software.}

@@

In this paper we propose CAFe: \emph{Co-Array Fortran Extensions}.  These extensions to CAF introduce
relatively minor additions to the existing coarray portion of the Fortran language.  They
include the concept of subimages in order to nest coarray images, semantics for distributed
array declarations, memory placement, remote memory transfer, and remote task execution
and synchronization.  CAFe
builds upon the existing standardized coarray features of Fortran.  We will introduce the
proposed CAFe extensions, define their semantics, demonstrate their use in a simple
example, and provide experimental results demonstrating the relative
performance of computation and communication in a prototype implementation executing
in a heterogeneous environment.
CAFe is complementary to
previous work extending coarray Fortran\cite{mellor-crummey:2009:caf2,jin:2011:caf2}.
